\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-11-23 Final Paper/PaperJLin.tex
Added discussion about the Electoral formula and drafted conclusion

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Issue Stances - General Trends}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Worldwide} \\
		\hline 
		Small Town&-.1005*** \\
		&(.0136)\\
		Suburban&-.1737***\\
		&(.0162) \\
		Urban&-.1306*** \\
		&(.0123)\\
		Constant&5.7164*** \\
		&(.0093) \\
		N&42,500 \\
		$R^2$&0.0037 \\
		\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table14}
\end{table}

@@

@@

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &-.1000***&-.0018 \\
	&(.0339)&(.0130) \\
	Suburban& -.1517***& .0147 \\
	&(.0401)& (.0157) \\
	Urban&-.0517* & -.0420*** \\
	&(.0304) & (.0117) \\
	\e{Democracy}& -.1995*** & -.0421***\\
	&(.0110) & (.0040)\\
	\e{Regime Age} & -.0014*** &  -.0075***\\
	&(.0002) & (.0001)\\
	\e{Electoral Formula}&.0778*** & -.0440***\\
	&(.0189) & (.0070) \\
	\hline
	Constant& 7.3627*** & 6.5149*** \\
	&(.1067) & (.0391)\\
	N&46,555 & 41,373 \\
	$R^2$&0.0135& 0.1273 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{\tb{Ideology In Each Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
		\hline
		Small Town&-.6640*** &.0608 &-.1600** \\
		&(.0766)&(.0435) &(.0727) \\
		Suburban&-.6389*** &-.1894***&-.1260  \\
		&(.1042) &(.0451) &(.1180) \\
		Urban&-.5781*** &-.0327 &.2655*** \\
		&(.0710) &(.0388) &(.0644) \\
		Constant& 5.8256*** &5.5408***&5.5562*** \\
		&(.0543) &(.0297) &(.0531) \\
		Countries&5&21&6 \\
		N&8,350&28,869 &10,602 \\
		$R^2$&0.0114&0.0011 &0.0052 \\
		\hline 
	\end{tabulary} 
\\ 
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table16}
\end{table}

Table \ref{table16} shows the relationship of place of residence in countries grouped by their electoral formula.

@@

From the results of the data analyses, we can see that...

@@

>>>>

\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Issue Stances - General Trends}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Worldwide} \\
		\hline 
		Small Town&-.1005*** \\
		&(.0136)\\
		Suburban&-.1737***\\
		&(.0162) \\
		Urban&-.1306*** \\
		&(.0123)\\
		Constant&5.7164*** \\
		&(.0093) \\
		N&42,500 \\
		$R^2$&0.0037 \\
		\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table14}
\end{table}

@@

However, the results here provide an interesting deviation from the patterns that are observed using self-placement on the ideology spectrum as a dependent variable. Here, a higher score indicates that individuals will be \e{more} liberal when it comes to government spending on social policy. As noted earlier, residets of urban centers tend to see themselves as more left-leaning, but they are relatively less interested in seeing government spend more money on health care, defense, and other social welfare measures that would ensure equity among the people in the country.

@@

\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &-.1000***&-.0018 \\
	&(.0339)&(.0130) \\
	Suburban& -.1517***& .0147 \\
	&(.0401)& (.0157) \\
	Urban&-.0517* & -.0420*** \\
	&(.0304) & (.0117) \\
	\e{Democracy}& -.1995*** & -.0421***\\
	&(.0110) & (.0040)\\
	\e{Regime Age} & -.0014*** &  -.0075***\\
	&(.0002) & (.0001)\\
	\e{Electoral Formula}&.0778*** & -.0440***\\
	&(.0189) & (.0070) \\
	\hline
	Constant& 7.3627*** & 6.5149*** \\
	&(.1067) & (.0391)\\
	N&46,555 & 41,373 \\
	$R^2$&0.0135& 0.1273 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

\begin{table}[h!]
	\centering
	\caption{\tb{Ideology In Each Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
		\hline
		Small Town&-.6640*** &.0608 &-.1600** \\
		&(.0766)&(.0435) &(.0727) \\
		Suburban&-.6389*** &-.1894***&-.1260  \\
		&(.1042) &(.0451) &(.1180) \\
		Urban&-.5781*** &-.0327 &.2655*** \\
		&(.0710) &(.0388) &(.0644) \\
		Constant& 5.8256*** &5.5408***&5.5562*** \\
		&(.0543) &(.0297) &(.0531) \\
		Countries&5&21&6 \\
		N&8,350&28,869 &10,602 \\
		$R^2$&0.0114&0.0011 &0.0052 \\
		\hline 
	\end{tabulary} 
\\ 
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table16}
\end{table}

Table \ref{table16} shows the relationship of place of residence in countries grouped by their electoral formula. By the differences in the results, we can see that the electoral formula matters in the relationship between place of residence and political attitudes.

Majoritarian elections are defined by first-past-the-post result tabulations where the candidate with the most votes is tapped as the winner of the race. With this campaign method, there is space of candidates to appeal to certain constituencies strategically to gain the most votes for themselves. In theory, a large representative body should serve different interests, but reality is hard to match expectations. Therefore, candidates and voters alike must push for their own interests to dominate, making a polarized electorate more likely on the lines of differing interest \cite{abramowitz-2010}. The results confirms this expectation. Individuals living in small towns, suburban and urban areas are significantly mor likely to lean left than their rural counterparts. While the differences among each other is not as big of a difference, it is significantly different from a rural place of residence.

Proportional representation occurs when parties are able to allocate votes in ratio to the number of votes that they receive. Therefore, it becomes more likely that different interests are represented in practice and that minority parties will have a chance in policymaking. This may help explain the insignificant results for the differences in places of residence on political attitudes when the countries are aggregated. However, in our previous discussions, proportional countries also see significant differences between places of residence, with Israel and Greece in 2012. However, this aggregate pattern carries for most of the other proportional representation states in this study.

Finally, a mixed representation system has combinations of the aforementioned systems. When aggregated, there are differences between place of residence and political attitudes. Depending on the specifications of the government design in each country, there can be great variations between countries and levels of significance. While the urban-rural divide is significant in Germany, it is not so in Japan.

To conclude, we see that the electoral formula matters in shaping political competition and electoral appeals from the perspective of the party. However, there are not clear distinctions for formulas such that it is a tell-all third factor in explaining the relationship between place and political attitudes.

@@

From the results of the data analyses, we can see that there are general relationships between place and political attitudes. However, when we dive deeper into the individuality of each country, we see that the idiosyncrasies that define each polity makes this a hard generalization to make.

@@

The goal of this paper is not to make generalizations about how people who live in suburbia around the world compare to those in the rural countryside when it comes to political attitudes, rather, it is to gain a general understanding of how the variables of place and political attitudes relate on a broad and specific level. From the data, I can draw the following conclusions. First, place matters. In the \e{Place Matters} hypothesis, the results confirm the findings such that urban residents, on average, differ from their rural counterparts when it comes to political ideology. The results confirm that urban residents, along with small town and suburban residents, tend to be more left leaning than their rural counterparts. However, the average difference between urban and rural, suburban and rural, and even small town and rural, are not necessarily increasing as one moves towards the city. Residents of the global suburbia, on average, see themselves to be more left leaning than their urban counterparts.

Second, the \e{Issue Stances} hypothesis is supported by the data because a person's place of residence does influence how one conceptualizes the issues and rate their support. However, as seen in Table \ref{table14}, urban residents are, on average, more conservative on their willingness to spend public dollars than their rural counterparts. This comes in contrast with the results in the \e{Place Matters} hypothesis. While urban residents may see themselves as more left leaning, they may have other motivations to limit their support for social and economic policy.

Finally, in Hypothesis 3, we examine the macro variables that are part of defining major democratic aspects of each country.
